---
title: "Normalisation - Imputation - Combining data sets - PART 3"
output:
  html_document:
    df_print: paged
  pdf_document: default
header-includes: "\\usepackage[export]{adjustbox}\n\\let\\includegraphicsbak\\includegraphics\n\\renewcommand*{\\includegraphics}[2][]{\\includegraphicsbak[frame,#1]{#2}}
  \n"
---
# Beta and M value distributions autosomal chromosomes

### QN normalised autosomal probes

```{r, out.width="400px", out.height="400px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/beta_distribution_filtered_QN_1e16.pdf"))
```

### QN & BMIQ normalised autosomal probes

```{r, out.width="400px", out.height="400px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/beta_distribution_filtered_QN_BMIQ_1e16.pdf"))
```

### Final beta values of autosomal probes - normalised and imputed

```{r, out.width="400px", out.height="400px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Beta_distribution_final_autosomes.pdf"))
```

### Final M values of autosomal probes - normalised and imputed 

```{r, out.width="400px", out.height="400px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/Distributions/Mvalue_distribution_final_autosomes.pdf"))
```

# Outlier detection

```{r, out.width="400px", out.height="400px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/PCA_FINAL_Mvalues.pdf"))
```

# Batch effects

```{r, out.width="800px", out.height="1600px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/PCA_final_Groups.pdf"))
```

# Ancestry prediction

### PCA of array snp probes combined with 0 BP SNP probes coloured by ancestry

```{r, out.width="400px", out.height="400px", message=FALSE, echo=FALSE}
knitr::include_graphics(file.path(dir_gen,"output/Figures/PCA_Ancestry.pdf"))
```

